\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/paper.tex
intergenerational -> inter-generational

For further details, browse the directory \code{examples/tower/}.
One can build and run the example therein by:
\begin{numlstlisting}
$ cd examples/tower
$ make
$ ./run_tower.x --slha-input-file=LesHouches.in.tower
\end{numlstlisting}%% $
In the output,
a part of significant physical interest might be:
\begin{numlstlisting}
Block MSL2 Q=   8.97114431E+02
  1  1     1.25652698E+05   # ml2(1,1)
  1  2    -7.64196328E+01   # ml2(1,2)
  1  3    -7.08429254E+01   # ml2(1,3)
  2  1    -7.64196328E+01   # ml2(2,1)
  2  2     1.25388732E+05   # ml2(2,2)
  2  3    -3.15865242E+02   # ml2(2,3)
  3  1    -7.08429254E+01   # ml2(3,1)
  3  2    -3.15865242E+02   # ml2(3,2)
  3  3     1.24556532E+05   # ml2(3,3)
\end{numlstlisting}
This result demonstrates the well-known effect on
the off-diagonal slepton mass matrix elements
from a non-trivial flavour structure of \code{Yv}
\cite{Borzumati:1986qx}.
This leads in turn to the slepton mixing
matrices, \code{ZE} and \code{ZV},
which contain intergenerational mixings apart from the
generic left-right mixings.

>>>>

For further details, browse the directory \code{examples/tower/}.
One can build and run the example therein by:
\begin{numlstlisting}
$ cd examples/tower
$ make
$ ./run_tower.x --slha-input-file=LesHouches.in.tower
\end{numlstlisting}%% $
In the output,
a part of significant physical interest might be:
\begin{numlstlisting}
Block MSL2 Q=   8.97114431E+02
  1  1     1.25652698E+05   # ml2(1,1)
  1  2    -7.64196328E+01   # ml2(1,2)
  1  3    -7.08429254E+01   # ml2(1,3)
  2  1    -7.64196328E+01   # ml2(2,1)
  2  2     1.25388732E+05   # ml2(2,2)
  2  3    -3.15865242E+02   # ml2(2,3)
  3  1    -7.08429254E+01   # ml2(3,1)
  3  2    -3.15865242E+02   # ml2(3,2)
  3  3     1.24556532E+05   # ml2(3,3)
\end{numlstlisting}
This result demonstrates the well-known effect on
the off-diagonal slepton mass matrix elements
from a non-trivial flavour structure of \code{Yv}
\cite{Borzumati:1986qx}.
This leads in turn to the slepton mixing
matrices, \code{ZE} and \code{ZV},
which contain inter-generational mixings apart from the
generic left-right mixings.
